A weakly structured stem for human origins in Africa

### 2023-02-24 paper.tex
added author contributions draft

\section*{Author contributions}
\aprcomment{To do: fill in (e.g., designed the study, collected data,
analyzed data, wrote and edited the manuscript)}
\begin{itemize}
    \item APR:
    \item TDW:
    \item EGA: 
    \item EH:
    \item MM:
    \item BMH:
    \item SG:
\end{itemize}

>>>>

\section*{Author contributions}
\aprcomment{To do: fill in (e.g., designed the study, collected data,
analyzed data, wrote and edited the manuscript)}
\sgcomment{Very rough first pass:}
APR, BMH, and SG designed the study. BMH, EGA, EH, and MM designed and conducted 
participant recruitment.   APR, BMH, and SG designed statistical analyses.
APR conducted statistical analyses. 
APR, TDW, BMH, and SG interpreted the results and wrote the first draft of the article. 
All authors read and edited the article.
